\Title

### 2020-03-10 manuscript/manuscript.tex
Replace Bellow for Below on LaTeX variable name

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/source-layouts-schematics.pdf}
    \caption{
        Source layouts.
        (a) Set of \SourceLayoutsSchematicsObservations{} synthetic observation
            points that resemble a ground survey.
        (b) Location of the \SourceLayoutsSchematicsSourceBellowData{} sources
            obtained through the \emph{sources beneath data} layout.
        (c) Location of the \SourceLayoutsSchematicsBlockMedianSources{}
            sources obtained through the \emph{block averaged sources} layout.
        (d) Location of the \SourceLayoutsSchematicsGridSources{} sources
            obtained through the \emph{grid sources} layout.
    }
    \label{fig:source-layouts-schematics}
\end{figure*}

@@

        \textbf{Constant depth} & & & \\
        \hline
        Depth (m) & \BestAirborneSourceBelowDataConstantDepthDepth
                   & \BestAirborneBlockMedianSourcesConstantDepthDepth
                   & \BestAirborneGridSourcesConstantDepthDepth \\
        Spacing (m) & -
                     & \BestAirborneBlockMedianSourcesConstantDepthSpacing
                     & \BestAirborneGridSourcesConstantDepthSpacing \\
        Pad & -
            & -
            & \BestAirborneGridSourcesConstantDepthPad \\
        Damping & \BestAirborneSourceBelowDataConstantDepthDamping
                & \BestAirborneBlockMedianSourcesConstantDepthDamping
                & \BestAirborneGridSourcesConstantDepthDamping \\
        R$^2$ score & \BestAirborneSourceBelowDataConstantDepthScore
                    & \BestAirborneBlockMedianSourcesConstantDepthScore
                    & \BestAirborneGridSourcesConstantDepthScore \\
        \textbf{R$^2$ score}
                & \textbf{\BestAirborneSourceBelowDataConstantDepthScore}
                & \textbf{\BestAirborneBlockMedianSourcesConstantDepthScore}
                & \textbf{\BestAirborneGridSourcesConstantDepthScore} \\

@@

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic ground survey.
    }
    \label{tab:parameters-ground-survey}
    \begin{tabular}{l c c c}
        & \textbf{Sources below data} & \textbf{Block median sources}
        & \textbf{Grid sources} \\

        \textbf{Constant depth} & & & \\
        \hline
        Depth (km) & \GroundSourceBelowDataConstantDepthDepth
                   & \GroundBlockMedianSourcesConstantDepthDepth
                   & \GroundGridSourcesConstantDepthDepth \\
        Spacing (km) & -
                     & \GroundBlockMedianSourcesConstantDepthSpacing
                     & \GroundGridSourcesConstantDepthSpacing \\
        Pad & -
            & -
            & \GroundGridSourcesConstantDepthPad \\

        & & & \\
        \textbf{Relative depth} & & & \\
        \cline{1-3}
        Depth (km) & \GroundSourceBelowDataRelativeDepthDepth
                   & \GroundBlockMedianSourcesRelativeDepthDepth
                   & \\
        Spacing (km) & -
                & \GroundBlockMedianSourcesRelativeDepthSpacing
                & \\

        & & & \\
        \textbf{Variable depth} & & & \\
        \cline{1-3}
        Depth (km) & \GroundSourceBelowDataVariableDepthDepth
                   & \GroundBlockMedianSourcesVariableDepthDepth
                   & \\
        Depth factor & \GroundSourceBelowDataVariableDepthDepthFactor
                     & \GroundBlockMedianSourcesVariableDepthDepthFactor
                     & \\
        K nearest & \GroundSourceBelowDataVariableDepthKNearest
                  & \GroundBlockMedianSourcesVariableDepthKNearest
                  & \\
        Spacing (km) & -
                     & \GroundBlockMedianSourcesVariableDepthSpacing
                     & \\
    \end{tabular}
\end{table*}

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic airborne survey.
    }
    \label{tab:parameters-airborne-survey}
    \begin{tabular}{l c c c}
        & \textbf{Sources below data} & \textbf{Block median sources}
        & \textbf{Grid sources} \\

        \textbf{Constant depth} & & & \\
        \hline
        Depth (km) & \AirborneSourceBelowDataConstantDepthDepth
                   & \AirborneBlockMedianSourcesConstantDepthDepth
                   & \AirborneGridSourcesConstantDepthDepth \\
        Spacing (km) & -
                     & \AirborneBlockMedianSourcesConstantDepthSpacing
                     & \AirborneGridSourcesConstantDepthSpacing \\
        Pad & -
            & -
            & \AirborneGridSourcesConstantDepthPad \\

        & & & \\
        \textbf{Relative depth} & & & \\
        \cline{1-3}
        Depth (km) & \AirborneSourceBelowDataRelativeDepthDepth
                   & \AirborneBlockMedianSourcesRelativeDepthDepth
                   & \\
        Spacing (km) & -
                     & \AirborneBlockMedianSourcesRelativeDepthSpacing
                     & \\

        & & & \\
        \textbf{Variable depth} & & & \\
        \cline{1-3}
        Depth (km) & \AirborneSourceBelowDataVariableDepthDepth
                   & \AirborneBlockMedianSourcesVariableDepthDepth
                   & \\
        Depth factor & \AirborneSourceBelowDataVariableDepthDepthFactor
                     & \AirborneBlockMedianSourcesVariableDepthDepthFactor
                     & \\
        K nearest & \AirborneSourceBelowDataVariableDepthKNearest
                  & \AirborneBlockMedianSourcesVariableDepthKNearest
                  & \\
        Spacing (km) & -
                     & \AirborneBlockMedianSourcesVariableDepthSpacing
                     & \\
    \end{tabular}
\end{table*}

>>>>

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/source-layouts-schematics.pdf}
    \caption{
        Source layouts.
        (a) Set of \SourceLayoutsSchematicsObservations{} synthetic observation
            points that resemble a ground survey.
        (b) Location of the \SourceLayoutsSchematicsSourceBelowData{} sources
            obtained through the \emph{sources beneath data} layout.
        (c) Location of the \SourceLayoutsSchematicsBlockMedianSources{}
            sources obtained through the \emph{block averaged sources} layout.
        (d) Location of the \SourceLayoutsSchematicsGridSources{} sources
            obtained through the \emph{grid sources} layout.
    }
    \label{fig:source-layouts-schematics}
\end{figure*}

@@

        \textbf{Constant depth} & & & \\
        \hline
        Depth (m) & \BestAirborneSourceBelowDataConstantDepthDepth
                   & \BestAirborneBlockMedianSourcesConstantDepthDepth
                   & \BestAirborneGridSourcesConstantDepthDepth \\
        Spacing (m) & -
                     & \BestAirborneBlockMedianSourcesConstantDepthSpacing
                     & \BestAirborneGridSourcesConstantDepthSpacing \\
        Pad & -
            & -
            & \BestAirborneGridSourcesConstantDepthPad \\
        Damping & \BestAirborneSourceBelowDataConstantDepthDamping
                & \BestAirborneBlockMedianSourcesConstantDepthDamping
                & \BestAirborneGridSourcesConstantDepthDamping \\
        \textbf{R$^2$ score}
                & \textbf{\BestAirborneSourceBelowDataConstantDepthScore}
                & \textbf{\BestAirborneBlockMedianSourcesConstantDepthScore}
                & \textbf{\BestAirborneGridSourcesConstantDepthScore} \\

@@

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic ground survey.
    }
    \label{tab:parameters-ground-survey}
    \begin{tabular}{c c l c c c}
        \textbf{Source layout}
            & \textbf{Depth type}
            & \multicolumn{1}{c}{\textbf{Parameters}}
            & \textbf{Values}
            & \textbf{Best}
            & \textbf{R$^2$ score} \\
        \toprule

        \multirow{8}{*}{Source Bellow Data}
            & \multirow{2}{*}{Constant Depth}
                & Depth (m)
                & \GroundSourceBellowDataConstantDepthDepth
                  \GroundSourceBellowDataConstantDepthDepthIncrement
                & \BestGroundSourceBellowDataConstantDepthDepth
                & \multirow{2}{*}{
                    \BestGroundSourceBellowDataConstantDepthScore
                  } \\
            &
                & Damping
                & \GroundSourceBellowDataConstantDepthDamping
                  \GroundSourceBellowDataConstantDepthDampingIncrement
                & \BestGroundSourceBellowDataConstantDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{2}{*}{Relative Depth}
                & Depth (m)
                & \GroundSourceBellowDataRelativeDepthDepth
                  \GroundSourceBellowDataRelativeDepthDepthIncrement
                & \BestGroundSourceBellowDataRelativeDepthDepth
                & \multirow{2}{*}{
                    \BestGroundSourceBellowDataRelativeDepthScore
                  } \\
            &
                & Damping
                & \GroundSourceBellowDataRelativeDepthDamping
                  \GroundSourceBellowDataRelativeDepthDampingIncrement
                & \BestGroundSourceBellowDataRelativeDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{4}{*}{Variable Depth}
                & Depth (m)
                & \GroundSourceBellowDataVariableDepthDepth
                  \GroundSourceBellowDataVariableDepthDepthIncrement
                & \BestGroundSourceBellowDataVariableDepthDepth
                & \multirow{4}{*}{
                    \BestGroundSourceBellowDataVariableDepthScore
                  } \\
            &
                & Depth factor
                & \GroundSourceBellowDataVariableDepthDepthFactor
                  \GroundSourceBellowDataVariableDepthDepthFactorIncrement
                & \BestGroundSourceBellowDataVariableDepthDepthFactor
                & \\
            &
                & K nearest
                & \GroundSourceBellowDataVariableDepthKNearest
                  \GroundSourceBellowDataVariableDepthKNearestIncrement
                & \BestGroundSourceBellowDataVariableDepthKNearest
                & \\
            &
                & Damping
                & \GroundSourceBellowDataVariableDepthDamping
                  \GroundSourceBellowDataVariableDepthDampingIncrement
                & \BestGroundSourceBellowDataVariableDepthDamping
                & \\
        \midrule

        \multirow{11}{*}{Block median sources}
            & \multirow{3}{*}{Constant Depth}
                & Depth (m)
                & \GroundBlockMedianSourcesConstantDepthDepth
                  \GroundBlockMedianSourcesConstantDepthDepthIncrement
                & \BestGroundBlockMedianSourcesConstantDepthDepth
                & \multirow{3}{*}{
                    \BestGroundBlockMedianSourcesConstantDepthScore
                  } \\
            &
                & Spacing (m)
                & \GroundBlockMedianSourcesConstantDepthSpacing
                  \GroundBlockMedianSourcesConstantDepthSpacingIncrement
                & \BestGroundBlockMedianSourcesConstantDepthSpacing
                & \\
            &
                & Damping
                & \GroundBlockMedianSourcesConstantDepthDamping
                  \GroundBlockMedianSourcesConstantDepthDampingIncrement
                & \BestGroundBlockMedianSourcesConstantDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{3}{*}{Relative Depth}
                & Depth (m)
                & \GroundBlockMedianSourcesRelativeDepthDepth
                  \GroundBlockMedianSourcesRelativeDepthDepthIncrement
                & \BestGroundBlockMedianSourcesRelativeDepthDepth
                & \multirow{3}{*}{
                    \BestGroundBlockMedianSourcesRelativeDepthScore
                  } \\
            &
                & Spacing (m)
                & \GroundBlockMedianSourcesRelativeDepthSpacing
                  \GroundBlockMedianSourcesRelativeDepthSpacingIncrement
                & \BestGroundBlockMedianSourcesRelativeDepthSpacing
                & \\
            &
                & Damping
                & \GroundBlockMedianSourcesRelativeDepthDamping
                  \GroundBlockMedianSourcesRelativeDepthDampingIncrement
                & \BestGroundBlockMedianSourcesRelativeDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{5}{*}{Variable Depth}
                & Depth (m)
                & \GroundBlockMedianSourcesVariableDepthDepth
                  \GroundBlockMedianSourcesVariableDepthDepthIncrement
                & \BestGroundBlockMedianSourcesVariableDepthDepth
                & \multirow{5}{*}{
                    \BestGroundBlockMedianSourcesVariableDepthScore
                  } \\
            &
                & Depth factor
                & \GroundBlockMedianSourcesVariableDepthDepthFactor
                  \GroundBlockMedianSourcesVariableDepthDepthFactorIncrement
                & \BestGroundBlockMedianSourcesVariableDepthDepthFactor
                & \\
            &
                & K nearest
                & \GroundBlockMedianSourcesVariableDepthKNearest
                  \GroundBlockMedianSourcesVariableDepthKNearestIncrement
                & \BestGroundBlockMedianSourcesVariableDepthKNearest
                & \\
            &
                & Spacing (m)
                & \GroundBlockMedianSourcesVariableDepthSpacing
                  \GroundBlockMedianSourcesVariableDepthSpacingIncrement
                & \BestGroundBlockMedianSourcesVariableDepthSpacing
                & \\
            &
                & Damping
                & \GroundBlockMedianSourcesVariableDepthDamping
                  \GroundBlockMedianSourcesVariableDepthDampingIncrement
                & \BestGroundBlockMedianSourcesVariableDepthDamping
                & \\
        \midrule

        \multirow{4}{*}{Grid Sources}
            & \multirow{4}{*}{Constant Depth}
                & Depth (m)
                & \GroundGridSourcesConstantDepthDepth
                  \GroundGridSourcesConstantDepthDepthIncrement
                & \BestGroundGridSourcesConstantDepthDepth
                & \multirow{4}{*}{
                    \BestGroundGridSourcesConstantDepthScore
                  } \\
            &
                & Spacing (m)
                & \GroundGridSourcesConstantDepthSpacing
                  \GroundGridSourcesConstantDepthSpacingIncrement
                & \BestGroundGridSourcesConstantDepthSpacing
                & \\
            &
                & Pad
                & \GroundGridSourcesConstantDepthPad
                  \GroundGridSourcesConstantDepthPadIncrement
                & \BestGroundGridSourcesConstantDepthPad
                & \\
            &
                & Damping
                & \GroundGridSourcesConstantDepthDamping
                  \GroundGridSourcesConstantDepthDampingIncrement
                & \BestGroundGridSourcesConstantDepthDamping
                & \\
    \end{tabular}
\end{table*}

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic airborne survey.
    }
    \label{tab:parameters-airborne-survey}
    \begin{tabular}{c c l c}
        \textbf{Source layout}
            & \textbf{Depth type}
            & \multicolumn{1}{c}{\textbf{Parameters}}
            & \textbf{Values} \\
        \toprule

        \multirow{8}{*}{Source Bellow Data}
            & \multirow{2}{*}{Constant Depth}
                & Depth (m)
                & \AirborneSourceBellowDataConstantDepthDepth
                  \AirborneSourceBellowDataConstantDepthDepthIncrement \\
            &
                & Damping
                & \AirborneSourceBellowDataConstantDepthDamping
                  \AirborneSourceBellowDataConstantDepthDampingIncrement \\
            \cmidrule{2-4}
            & \multirow{2}{*}{Relative Depth}
                & Depth (m)
                & \AirborneSourceBellowDataRelativeDepthDepth
                  \AirborneSourceBellowDataRelativeDepthDepthIncrement \\
            &
                & Damping
                & \AirborneSourceBellowDataRelativeDepthDamping
                  \AirborneSourceBellowDataRelativeDepthDampingIncrement \\
            \cmidrule{2-4}
            & \multirow{4}{*}{Variable Depth}
                & Depth (m)
                & \AirborneSourceBellowDataVariableDepthDepth
                  \AirborneSourceBellowDataVariableDepthDepthIncrement \\
            &
                & Depth factor
                & \AirborneSourceBellowDataVariableDepthDepthFactor
                  \AirborneSourceBellowDataVariableDepthDepthFactorIncrement \\
            &
                & K nearest
                & \AirborneSourceBellowDataVariableDepthKNearest
                  \AirborneSourceBellowDataVariableDepthKNearestIncrement \\
            &
                & Damping
                & \AirborneSourceBellowDataVariableDepthDamping
                  \AirborneSourceBellowDataVariableDepthDampingIncrement \\
        \midrule

        \multirow{11}{*}{Block median sources}
            & \multirow{3}{*}{Constant Depth}
                & Depth (m)
                & \AirborneBlockMedianSourcesConstantDepthDepth
                  \AirborneBlockMedianSourcesConstantDepthDepthIncrement \\
            &
                & Spacing (m)
                & \AirborneBlockMedianSourcesConstantDepthSpacing
                  \AirborneBlockMedianSourcesConstantDepthSpacingIncrement \\
            &
                & Damping
                & \AirborneBlockMedianSourcesConstantDepthDamping
                  \AirborneBlockMedianSourcesConstantDepthDampingIncrement \\
            \cmidrule{2-4}
            & \multirow{3}{*}{Relative Depth}
                & Depth (m)
                & \AirborneBlockMedianSourcesRelativeDepthDepth
                  \AirborneBlockMedianSourcesRelativeDepthDepthIncrement \\
            &
                & Spacing (m)
                & \AirborneBlockMedianSourcesRelativeDepthSpacing
                  \AirborneBlockMedianSourcesRelativeDepthSpacingIncrement \\
            &
                & Damping
                & \AirborneBlockMedianSourcesRelativeDepthDamping
                  \AirborneBlockMedianSourcesRelativeDepthDampingIncrement \\
            \cmidrule{2-4}
            & \multirow{5}{*}{Variable Depth}
                & Depth (m)
                & \AirborneBlockMedianSourcesVariableDepthDepth
                  \AirborneBlockMedianSourcesVariableDepthDepthIncrement \\
            &
                & Depth factor
                & \AirborneBlockMedianSourcesVariableDepthDepthFactor
                  \AirborneBlockMedianSourcesVariableDepthDepthFactorIncrement \\
            &
                & K nearest
                & \AirborneBlockMedianSourcesVariableDepthKNearest
                  \AirborneBlockMedianSourcesVariableDepthKNearestIncrement \\
            &
                & Spacing (m)
                & \AirborneBlockMedianSourcesVariableDepthSpacing
                  \AirborneBlockMedianSourcesVariableDepthSpacingIncrement \\
            &
                & Damping
                & \AirborneBlockMedianSourcesVariableDepthDamping
                  \AirborneBlockMedianSourcesVariableDepthDampingIncrement \\
        \midrule

        \multirow{4}{*}{Grid Sources}
            & \multirow{4}{*}{Constant Depth}
                & Depth (m)
                    & \AirborneGridSourcesConstantDepthDepth
                      \AirborneGridSourcesConstantDepthDepthIncrement \\
            &
                & Spacing (m)
                    & \AirborneGridSourcesConstantDepthSpacing
                      \AirborneGridSourcesConstantDepthSpacingIncrement \\
            &
                & Pad
                    & \AirborneGridSourcesConstantDepthPad
                      \AirborneGridSourcesConstantDepthPadIncrement \\
            &
                & Damping
                    & \AirborneGridSourcesConstantDepthDamping
                      \AirborneGridSourcesConstantDepthDampingIncrement \\
    \end{tabular}
\end{table*}
